### 2016-04-26 p00-ch00-intro/intro.tex
Update based on comments from Stijn

ABS~\cite{johnsen2012abs,hahnlehjlssw11} is a modeling language for concurrent objects and distributed systems.
ABS uses asynchronous communication among objects.
A message in ABS is bound to a method invocation;
this defines the interface of the sent messages.
In addition, ABS supports future values in its asynchronous communication.
ABS introduces \bfjtt{release} semantics that is based on co-operative scheduling of objects; 
i.e. similar to that of \emph{yield} in coroutines~\cite{creol:broch:owe}.
The ABS semantics is completely formalized by a structural operational semantics~\cite{plotkin:sos,abs:2012}.
This allows ABS models to take advantage of a wide range of static and dynamic analysis techniques~\cite{DBLP:journals/sttt/WongBBGGHMS15,DBLP:conf/cade/DinBH15,DBLP:conf/ifm/GiachinoGLLW13,DBLP:conf/tacas/AlbertAFGGMPR14}.
% 
Co-operative scheduling in ABS has been additionally extended for real-time scheduling with priorities and time constraints~\cite{bjork2013:rtabs,johnsen2012modeling}.
All the above characteristics make the ABS language an attractive choice if it
can be used as a programming language at industrial and business scale.
ABS has mainly developed as a modeling language;
for example, ABS does not support a common I/O API for files or networking,
and it does not provide a standard library of data structures.

JSR 166~\cite{jsr166} introduced a new concurrency model~\cite{DBLP:conf/java/Lea00} in Java 1.5.
The concurrency model lays the grounds to support for the actor model with asynchronous method calls.
This gave rise to various research to support actor model on Java~\cite{actor_frameworks_jvm:agha} and further extend Java as a functional programming language~\cite{odersky1997pizza,henkel2003discovering,nystrom2003polyglot,bracha1998making}.
From an industrial perspective, the development of the Java language from version 6 to version 8 experienced a slow pace that influenced the growth of businesses and justified alternatives.
Scala~\cite{odersky2004scala}, a dynamic, functional, and object-oriented language on JVM, rose to the challenge to fill the gap during the period between Java~7 and Java~8.
Java~8~\cite{jls8} released fundamental features such as lambda expressions that are essential for concurrency and functional programming.

@@

\begin{table}[t]
\centering
\begin{tabular}{p{7cm}p{3cm}p{3cm}}
\textsfb{Topic} & \textsfb{Part} & \textsfb{Chapter/Section}
\\ \toprule
{Formalization of the mapping from ABS to Java including the operational semantics and ABS co-operative scheduling in Java} & Programming Model (Part~\ref{p:model}) & Chapter~\ref{ch:p01:ch01} and \ref{ch:p01:ch02}
\\ \midrule
Design and implementation of ABS concurrency layer in Java & Implementation (Part~\ref{p:impl}) & Chapter~\ref{ch:p02:ch01} 
% and \ref{ch:p02:ch02}
\\ \midrule 
Monitoring method call sequences using annotations & Application (Part~\ref{p:app}) & Chapter~\ref{ch:p03:ch02}
\\ \midrule
Design and implementation of a massive-scale monitoring system based on ABS API in Java & Application (Part~\ref{p:app}) & Chapter~\ref{ch:p03:ch01}
\\ \bottomrule 
\end{tabular}
\caption{Thesis Organization}
\label{tbl:thesis}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{p{2cm}p{7cm}p{1cm}}
\textsfb{Topic} & \textsfb{Proceedings / Journal} & \textsfb{Year}   
\\ \toprule
Chapter~\ref{ch:p01:ch01} & ACM SAC 2012, Pages 1883--1888 & 2012 
\\ \midrule
Chapter~\ref{ch:p01:ch02} & COORD 2013, Pages 181--195 & 2013 
\\ \midrule
Chapter~\ref{ch:p02:ch01} & ISoLA 2014, Pages 37--53 & 2014 
\\ \midrule
Chapter~\ref{ch:p03:ch02} & Journal of Science of Computer Programming, 2014, Volume 94, Part 3, Pages 362--378 & 2014 
\\ \midrule
Chapter~\ref{ch:p03:ch01} & ESOCC 2015, Pages 125--140 & 2015
\\ \bottomrule
\end{tabular}
\caption{Actors At Work -- Conference and Journal Publications}
\label{tbl:papers}
\end{table}

>>>>

ABS~\cite{johnsen2012abs,hahnlehjlssw11} is a modeling language for concurrent objects and distributed systems.
ABS uses asynchronous communication among objects.
A message in ABS is generated from a method enclosed by an interface.
this defines the interface of the sent messages.
In addition, ABS supports future values in its asynchronous communication.
ABS introduces \bfjtt{release} semantics that is based on co-operative scheduling of objects; 
i.e. similar to that of \emph{yield} in coroutines~\cite{creol:broch:owe}.
The ABS semantics is completely formalized by a structural operational semantics~\cite{plotkin:sos,abs:2012}.
This allows ABS models to take advantage of a wide range of static and dynamic analysis techniques~\cite{DBLP:journals/sttt/WongBBGGHMS15,DBLP:conf/cade/DinBH15,DBLP:conf/ifm/GiachinoGLLW13,DBLP:conf/tacas/AlbertAFGGMPR14}.
% 
Co-operative scheduling in ABS has been additionally extended for real-time scheduling with priorities and time constraints~\cite{bjork2013:rtabs,johnsen2012modeling}.
All the above characteristics make the ABS language an attractive choice if it
can be used as a programming language at industrial and business scale.
ABS has mainly developed as a modeling language;
for example, ABS does not support a common I/O API for files or networking,
and it does not provide a standard library of data structures.

JSR 166~\cite{jsr166} introduced a new concurrency model~\cite{DBLP:conf/java/Lea00} in Java 1.5.
The concurrency model lays the grounds to support for the actor model with asynchronous method calls.
This gave rise to various research to support actor model on Java~\cite{actor_frameworks_jvm:agha} and further extend Java as a functional programming language~\cite{odersky1997pizza,henkel2003discovering,nystrom2003polyglot,bracha1998making}.
From an industrial perspective, the development of the Java language from version 6 to version 8 experienced a slow pace that influenced the growth of businesses and justified alternatives.
Scala~\cite{odersky2004scala}, a dynamic, functional, and object-oriented language on JVM, rose to the challenge to fill the gap during the period between Java~7 and Java~8.
Java~8~\cite{jls8} alleviated this gap by releasing fundamental features such as lambda expressions that are essential for concurrency and functional programming.

@@

\begin{table}[t]
\centering
\begin{tabular}{p{7cm}p{3cm}p{3cm}}
\textsfb{Topic} & \textsfb{Part} & \textsfb{Chapter/Section}
\\ \toprule
{Formalization of the mapping from ABS to Java including the operational semantics and ABS co-operative scheduling in Java} & Programming Model (Part~\ref{p:model}) & Chapter~\ref{ch:p01:ch01} and \ref{ch:p01:ch02}
\\ \midrule
Design and implementation of ABS concurrency layer in Java & Implementation (Part~\ref{p:impl}) & Chapter~\ref{ch:p02:ch01} 
% and \ref{ch:p02:ch02}
\\ \midrule 
Monitoring method call sequences using annotations & Application (Part~\ref{p:app}) & Chapter~\ref{ch:p03:ch02}
\\ \midrule
Design and implementation of a massive-scale monitoring system based on ABS API in Java & Application (Part~\ref{p:app}) & Chapter~\ref{ch:p03:ch01}
\\ \bottomrule 
\end{tabular}
\caption{\thesisTitle -- Thesis Organization}
\label{tbl:thesis}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{p{2cm}p{7cm}p{1cm}}
\textsfb{Topic} & \textsfb{Proceedings / Journal} & \textsfb{Year}   
\\ \toprule
Chapter~\ref{ch:p01:ch01} & ACM SAC 2012, pp. 1883--1888 & 2012 
\\ \midrule
Chapter~\ref{ch:p01:ch02} & COORD 2013, pp. 181--195 & 2013 
\\ \midrule
Chapter~\ref{ch:p02:ch01} & ISoLA 2014, pp. 37--53 & 2014 
\\ \midrule
Chapter~\ref{ch:p03:ch02} & 
FACS 2010, pp. 53--70 \emph{and} 
\newline
Journal of Science of Computer Programming, vol. 94, part 3, pp. 362--378 & 
2010 \emph{and}
\newline
2014 
\\ \midrule
Chapter~\ref{ch:p03:ch01} & ESOCC 2015, pp. 125--140 & 2015
\\ \bottomrule
\end{tabular}
\caption{\thesisTitle -- Conference and Journal Publications}
\label{tbl:papers}
\end{table}
